Learning STRIPS action models with classical planning

### 2017-11-01 doc/icaps-18/strips-learning.tex
updated tables 5 and 6

\begin{table}[hbt!]
\begin{footnotesize}
	\begin{center}
		\begin{tabular}{l|l|l|l|l|l|l|}
			 & \multicolumn{2}{|c|}{\bf Pre} & \multicolumn{2}{|c|}{\bf Add} & \multicolumn{2}{|c|}{\bf Del}  \\ \cline{2-7}			
			  & \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} & \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} & \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} \\
			\hline
			Blocks & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 \\
			Driverlog & 1.0 & 0.4 & 1.0 & 1.0 & 1.0 & 0.7 \\
			Ferry & 1.0 & 0.6 & 0.5 & 1.0 & 1.0 & 1.0 \\
			Floortile & 0.5 & 0.6 & 1.0 & 0.8 & 1.0 & 0.8 \\
			Gripper & 1.0 & 0.5 & 1.0 & 1.0 & 1.0 & 1.0 \\
			Miconic & 1.0 & 0.2 & 1.0 & 1.0 & 1.0 & 1.0 \\
			Satellite & 1.0 & 0.5 & 0.5 & 1.0 & 1.0 & 1.0 \\
			Transport & 1.0 & 0.2 & 1.0 & 1.0 & 1.0 & 0.5 \\
			Zenotravel & 1.0 & 0.5 & 0.6 & 0.6 & 1.0 & 1.0
		\end{tabular}
	\end{center}
	\end{footnotesize}
\caption{\small The {\em precision} and {\em recall} values achieved by the learned models in the different domains.}
\label{tab:results_plans_partial}
\end{table}

\begin{table}[hbt!]
\begin{footnotesize}
	\begin{center}
		\begin{tabular}{l|c|c|c|}			
			Domain & Total time & Preprocess & Plan length  \\
			\hline
			Blocks & 0.07 & 0.01 & 54  \\
			Driverlog & 0.06 & 0.03 & 71 \\
			Ferry & 0.18 & 0.14 & 50 \\
			Floortile & 0.81 & 0.68 & 92 \\
			Gripper & 0.01 & 0.00 & 37 \\
			Miconic & 0.06 & 0.04 & 40  \\
			Satellite & 0.18 & 0.12 & 43 \\
			Transport & 0.15 & 0.14 & 33 \\
			Zenotravel & 2.54 & 2.54 & 42
		\end{tabular}
	\end{center}
        \end{footnotesize}
	\caption{\small Planning time, preprocessing time and Plan length.}
	\label{tab:time_plans_partial}	
\end{table}

>>>>

\begin{table}[hbt!]
\begin{footnotesize}
	\begin{center}
		\resizebox{\columnwidth}{!}{%
			\begin{tabular}{l|l|l|l|l|l|l|l|l|}
				& \multicolumn{2}{|c|}{\bf Pre} & \multicolumn{2}{|c|}{\bf Add} & \multicolumn{2}{|c|}{\bf Del} & \multicolumn{2}{|c|}{\bf All}\\ \cline{2-9}			
				& \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} & \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} & \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} &  \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} \\
				\hline
				Blocks & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 \\
				Driverlog & 1.0 & 0.71 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 0.91 \\
				Ferry & 1.0 & 0.67 & 0.5 & 1.0 & 1.0 & 1.0 & 0.83 & 0.89 \\
				Floortile & 0.75 & 0.60 & 1.0 & 0.80 & 1.0 & 0.80 & 0.92 & 0.73 \\
				Gripper & 1.0 & 0.50 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 0.83 \\
				Miconic & 1.0 & 0.75 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 0.92 \\
				Satellite & 1.0 & 0.57 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 0.86 \\
				Transport & 1.0 & 0.50 & 1.0 & 1.0 & 1.0 & 0.50 & 1.0 & 0.67 \\
%				Visitall & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 \\
				Zenotravel & 1.0 & 0.83 & 0.67 & 0.67 & 1.0 & 1.0 & 0.89 & 0.83 \\
				\hline
				\bf Total & 0.97 & 0.68 & 0.91 & 0.94 & 1.0 & 0.92 & 0.96 & 0.85 \\
			\end{tabular}
		}
	\end{center}
	\end{footnotesize}
\caption{\small The {\em precision} and {\em recall} values achieved by the learned models in the different domains.}
\label{tab:results_plans_partial}
\end{table}

\begin{table}[hbt!]
\begin{footnotesize}
	\begin{center}
		\begin{tabular}{l|c|c|c|}			
			Domain & Total time & Preprocess & Plan length  \\
			\hline
			Blocks & 0.07 & 0.01 & 54  \\
			Driverlog & 0.06 & 0.03 & 59 \\
			Ferry & 0.20 & 0.14 & 50 \\
			Floortile & 0.54 & 0.45 & 58 \\
			Gripper & 0.01 & 0.00 & 37 \\
			Miconic & 0.06 & 0.04 & 33  \\
			Satellite & 0.17 & 0.15 & 48 \\
			Transport & 0.12 & 0.10 & 33 \\
			Zenotravel & 0.26 & 0.26 & 33
		\end{tabular}
	\end{center}
        \end{footnotesize}
	\caption{\small Planning time, preprocessing time and Plan length.}
	\label{tab:time_plans_partial}	
\end{table}
